Supplementary Material for: A Rough Guide to Pre-processing High-Frequency Animal Tracking Data

### 2021-02-04 _03_smoothing_tracks.Rmd
change green and blue

# prepare a palette
pal <- RColorBrewer::brewer.pal(4, "Set1")
```

@@

```{r echo=FALSE}
### plot figures
fig_agg_data <-
  Map(
    function(df, title) {
      ggplot(df) +
        # geom_path(data = data,
        #           aes(x, y),
        #           col = "grey20",
        #           size = 0.2)+
        geom_point(
          data = data_agg,
          aes(x, y),
          size = 0.3,
          col = pal[3]
        ) +
        geom_path(aes(x, y),
          col = pal[4]
        ) +
        geom_point(aes(x, y,
          group = interval
        ),
        shape = 0,
        col = pal[4],
        alpha = 1,
        show.legend = F
        ) +
        ggthemes::theme_few() +
        theme(
          axis.text = element_blank(),
          axis.title = element_blank(),
          plot.title = element_text(
            face = "bold",
            margin = margin(t = 30, b = -30),
            hjust = 0.8
          )
        ) +
        coord_cartesian(ylim = c(0.6, NA)) +
        labs(
          title = sprintf("(%s)", title)
        )
    },
    list_of_agg,
    c(NA, NA, "a", "b")
  )
```

@@

# aggregate before correction
list_of_agg <- lapply(c(3, 10, 30, 120), function(z) {
  data_return <- atl_thin_data(
    data = data_errors,
    interval = z,
    method = "aggregate"
  )
  data_return[, interval := z]
  data_return[, speed := atl_get_speed(data_return)]
  return(data_return)
})

@@

@@

```{r}
# now plot distribution of speed
data_agg <- rbindlist(list_of_agg)
```

```{r echo=FALSE}
# show boxplot of speed
fig_agg_speed <-
  ggplot(data_agg) +
  geom_hline(
    yintercept =
      1 + quantile(data$speed,
        na.rm = T,
        probs = c(0.5, 0.95)
      ),
    lty = c(1, 2)
  ) +
  geom_errorbar(
    data = speed_agg_smooth,
    aes(
      x = factor(interval),
      ymin = 1 + median - sd,
      ymax = 1 + median + sd
    ),
    width = 0.2,
    position = position_nudge(x = 0.25)
  ) +
  geom_point(
    data = speed_agg_smooth,
    aes(
      x = factor(interval),
      y = 1 + median
    ),
    shape = 21,
    size = 3,
    fill = pal[3],
    position = position_nudge(x = 0.25)
  ) +
  geom_boxplot(aes(factor(interval), 1 + speed),
    position = position_nudge(x = -0.25, ),
    fill = "grey",
    alpha = 0.5,
    show.legend = F,
    width = 0.25,
    outlier.size = 0.2
  ) +
  scale_y_log10(
    label = scales::comma,
    limits = c(NA, 1.005)
  ) +
  ggthemes::theme_few() +
  theme(
    axis.text.y = element_blank(),
    axis.text = element_blank(),
    axis.title = element_blank(),
    plot.title = element_text(
      face = "bold",
      margin = margin(t = 30, b = -30),
      hjust = 0.8
    )
  ) +
  labs(
    x = "interval (s)",
    y = "speed",
    title = "(c)"
  )
```

```{r echo=FALSE}
# make combined figure
fig_aggregate <-
  wrap_plots(
    append(fig_agg_data[3:4], list(fig_agg_speed)),
    design = "AABBC"
  )

>>>>

# define a four colour palette
pal <- RColorBrewer::brewer.pal(5, "Set1")
pal[3] = "seagreen"
pal[2] = RColorBrewer::brewer.pal(5, "Blues")[5]
```

@@

### Plot of aggregation after smoothing

```{r echo=FALSE}
# prepare data
data_agg_smooth = copy(list_of_agg[[3]]) # 30s aggregate
### plot figures
fig_agg_data_smooth <-
      ggplot(data_agg_smooth) +
        geom_point(
          data = data_agg,
          size = 0.2,
          aes(x, y),
          col = pal[3]
        ) +
        geom_path(aes(x, y),
          col = pal[2],
          lwd = 0.2
        ) +
        geom_point(aes(x, y,
          group = interval
        ),
        shape = 1,
        size = 2,
        col = pal[2],
        alpha = 1,
        show.legend = F
        ) +
        ggthemes::theme_few() +
        theme(
          axis.text = element_blank(),
          axis.title = element_blank(),
          plot.title = element_text(
            face = "bold",
            margin = margin(t = 30, b = -30),
            hjust = 0.9
          )
        ) +
        coord_cartesian(ylim = c(0.6, NA)) +
        labs(
          title = "(a)"
        )
```

@@

# aggregate before correction
list_of_agg_errors <- lapply(c(3, 10, 30, 120), function(z) {
  data_return <- atl_thin_data(
    data = data_errors,
    interval = z,
    method = "aggregate"
  )
  data_return[, interval := z]
  data_return[, speed := atl_get_speed(data_return)]
  return(data_return)
})

@@

### Figure aggregation before smoothing

```{r echo=FALSE}
# prepare data
data_agg_error = copy(list_of_agg_errors[[3]]) # 30s aggregate
### plot figures
fig_agg_data_error <-
      ggplot(data_agg_error) +
        geom_point(
          data = data_errors,
          size = 0.1,
          aes(x, y),
          col = "grey"
        ) +
        geom_path(aes(x, y),
          col = pal[2]
          # lwd = 0.1
        ) +
        geom_point(aes(x, y,
          group = interval
        ),
        shape = 1,
        size = 2,
        col = pal[2],
        alpha = 1,
        show.legend = F
        ) +
        ggthemes::theme_few() +
        theme(
          axis.text = element_blank(),
          axis.title = element_blank(),
          plot.title = element_text(
            face = "bold",
            margin = margin(t = 30, b = -30),
            hjust = 0.9
          )
        ) +
        coord_cartesian(ylim = c(0.6, NA)) +
        labs(
          title = "(b)"
        )
```

@@

```{r}
# now plot distribution of speed
data_agg <- rbindlist(list_of_agg_errors)
```

```{r echo=FALSE}
# show boxplot of speed
fig_agg_speed <-
  ggplot(data_agg) +
  geom_hline(
    yintercept =
      1 + quantile(data$speed,
        na.rm = T,
        probs = c(0.5, 0.95)
      ),
    lty = c(1, 2)
  ) +
  geom_errorbar(
    data = speed_agg_smooth,
    aes(
      x = factor(interval),
      ymin = 1 + median - sd,
      ymax = 1 + median + sd
    ),
    width = 0.2,
    position = position_nudge(x = 0.25)
  ) +
  geom_point(
    data = speed_agg_smooth,
    aes(
      x = factor(interval),
      y = 1 + median
    ),
    shape = 21,
    size = 3,
    fill = pal[3],
    position = position_nudge(x = 0.25)
  ) +
  geom_boxplot(aes(factor(interval), 1 + speed),
    position = position_nudge(x = -0.25, ),
    fill = "grey",
    alpha = 0.5,
    show.legend = F,
    width = 0.25,
    outlier.size = 0.2
  ) +
  scale_y_log10(
    label = scales::comma,
    limits = c(NA, 1.005)
  ) +
  ggthemes::theme_few() +
  theme(
    axis.text.y = element_blank(),
    plot.title = element_text(
      face = "bold",
      margin = margin(t = 30, b = -30),
      hjust = 0.8
    )
  ) +
  labs(
    x = "interval (s)",
    y = "speed",
    title = "(c)"
  )
```

```{r echo=FALSE}
# make combined figure
fig_aggregate <-
  wrap_plots(
    fig_agg_data_smooth, fig_agg_data_error, fig_agg_speed,
    design = "AABBC"
  )
